Competing Bandits

### 2017-12-03 Writeup/writeup.tex
update

We simulate this in the following scenario. We set $K = 10$

\section*{Experiment 5 - Warm Start and HardMax}
What is the effect of a ``warm start" on the performance of HardMax? Our simulations show that with HardMax the initial rounds matter a lot in a particular simulation and whoever wins in the first few rounds takes the entire market. We explore if having a warm start makes it so that the market is more evenly split in a given simulation.\\

>>>>

We simulate this in the following scenario. We set $K = 10$ where 8 of the arms have approximately identical means ($Bernoulli(0.45)$), one of the arms (denote it as arm $B$) has a higher mean ($Bernoulli(0.55)$), and we vary the mean of the ``best" arm (denote it as arm $A$) in increments of 0.1. Thus, we consider a simulation where $Bernoulli(0.55), Bernoulli(0.65), Bernoulli(0.75)$.

We suppose that the ``dumb" principal 2 has relatively correct beliefs in that she has a prior such that arm $B$ is the best arm. We suppose that the ``smart" principal 1 has perverse beliefs such that she has a prior that the 8 worst arms have the best mean reward ($Beta(0.45, 0.55)$), arm $B$ has slightly worse mean reward ($Beta(0.4, 0.6$), and arm $A$ has substantially worse mean reward ($Beta(0.1, 0.9)$).

We run simulations under this setup to see if the ``smart" principal's learning algorithm can let her overcome the bad beliefs.

\begin{center}
Agent: HardMax, T = 5000
 \begin{tabular}{||c c c c c c||} 
 \hline
 Mean of Arm A & Principal 1 Alg & Principal 1 MS & Principal 2 MS & Principal 1 Avg Regret & Principal 2 Avg Regret  \\ [0.5ex] 
 \hline\hline
 0.55 & ThompsonSampling & 0.440 & 0.560 & 0.049 & 0.00 \\ 
 \hline
 0.65 & ThompsonSampling & 0.647 & 0.353 &  0.057 &  0.100 \\
 \hline
 0.75 & ThompsonSampling & 0.710 & 0.291 & 0.059  & 0.200 \\
 \hline
 0.55 & Dynamic $\epsilon$-greedy & 0.298 & 0.656 & 0.057 & 0.000 \\
 \hline
  0.65 & Dynamic $\epsilon$-greedy & 0.335 & 0.664 & 0.138 & 0.100 \\
 \hline
  0.75 & Dynamic $\epsilon$-greedy & 0.442 & 0.558 & 0.154 & 0.200 \\[1ex]
  \hline
\end{tabular}
\end{center}
\vspace{0.75cm}
\begin{center}
Agent: HardMaxWithRandom, T = 5000
 \begin{tabular}{||c c c c c c||} 
 \hline
 Mean of Arm A & Principal 1 Alg & Principal 1 MS & Principal 2 MS & Principal 1 Avg Regret & Principal 2 Avg Regret  \\ [0.5ex] 
 \hline\hline
 0.55 & ThompsonSampling & 0.317 & 0.683 & 0.031 & 0.00 \\ 
 \hline
 0.65 & ThompsonSampling & 0.630 & 0.369 &  0.028 &  0.100 \\
 \hline
 0.75 & ThompsonSampling & 0.787 & 0.291 & 0.015  & 0.200 \\
 \hline
 0.55 & Dynamic $\epsilon$-greedy & 0.343 & 0.702 & 0.038 & 0.000 \\
 \hline
  0.65 & Dynamic $\epsilon$-greedy & 0.400 & 0.600 & 0.076 & 0.100 \\
 \hline
  0.75 & Dynamic $\epsilon$-greedy &0.615 & 0.385 & 0.074 & 0.200 \\[1ex]
  \hline
\end{tabular}
\end{center}

\vspace{0.75cm}
\begin{center}
Agent: SoftMax, T = 5000
 \begin{tabular}{||c c c c c c||} 
 \hline
 Mean of Arm A & Principal 1 Alg & Principal 1 MS & Principal 2 MS & Principal 1 Avg Regret & Principal 2 Avg Regret  \\ [0.5ex] 
 \hline\hline
 0.55 & ThompsonSampling & 0.442 & 0.558 & 0.027 & 0.00 \\ 
 \hline
 0.65 & ThompsonSampling & 0.600 & 0.400 &  0.025 &  0.100 \\
 \hline
 0.75 & ThompsonSampling & 0.721 & 0.280 & 0.026  & 0.200 \\
 \hline
 0.55 & Dynamic $\epsilon$-greedy & 0.442 & 0.556 & 0.038 & 0.000 \\
 \hline
  0.65 & Dynamic $\epsilon$-greedy & 0.400 & 0.600 & 0.021 & 0.100 \\
 \hline
  0.75 & Dynamic $\epsilon$-greedy & 0.666 & 0.334 & 0.050 & 0.200 \\[1ex]
  \hline
\end{tabular}
\end{center}
\vspace{0.25cm}
Regardless of the behavioral model of the agent, we see that the ``dumb" principal 2 wins a higher share of the market than principal 1 when she happens to have correct prior beliefs about the best arm. This happens whether principal 1 plays an adaptive or a non-adaptive exploration algorithm. Intuitively this makes sense as the ``dumb" principal will end up getting regret 0 simply because of her correct beliefs and it is incredibly hard for a smarter learning algorithm to make up for this. \\
\\
However, as we increase the reward of arm $A$ such that principal 2 no longer has completely correct beliefs (she believes the second-best arm is the best arm), we see that when principal 1 plays an adaptive exploration algorithm she catches up very quickly and takes most of the market. However, when principal 1 plays a non-adaptive exploration algorithm we see that the ``dumb" algorithm with better initial information still wins out, especially when the agent is HardMax. As we make the agent ``more behavioral", the non-adaptive exploration algorithm becomes progressively better.\\
\\
The previous results show that, especially when playing an adaptive exploration algorithm, it is possible that a better learning algorithm helps overcome initial bad information even if the opponent has almost correct information. However, one expects this takes time and that perhaps if we set $T$ to be lower, the ``dumb" principal would still win. To test this, we re-run the same simulations as above but set $T=500$

\begin{center}
Agent: HardMax, T = 500
 \begin{tabular}{||c c c c c c||} 
 \hline
 Mean of Arm A & Principal 1 Alg & Principal 1 MS & Principal 2 MS & Principal 1 Avg Regret & Principal 2 Avg Regret  \\ [0.5ex] 
 \hline\hline
 0.55 & ThompsonSampling & 0.181 & 0.812 & 0.088 & 0.0 \\
 \hline
 0.65 & ThompsonSampling & 0.287 & 0.712 & 0.178 &  0.100 \\
 \hline
 0.75 & ThompsonSampling & 0.274 & 0.723 & 0.244  & 0.200 \\
 \hline
 0.55 & Dynamic $\epsilon$-greedy & 0.183 & 0.817 & 0.100 & 0.000 \\
 \hline
  0.65 & Dynamic $\epsilon$-greedy & 0.169 & 0.831 & 0.190 & 0.100 \\
 \hline
  0.75 & Dynamic $\epsilon$-greedy & 0.297 & 0.703 & 0.251 & 0.200 \\[1ex]
  \hline
\end{tabular}
\end{center}
\vspace{0.25cm}
This demonstrates that part of the results from above were driven by the large $T$ and that with a low $T$ of 500, the ``smart" learning algorithm does not have enough time to overcome the bad initial information. Thus we conclude that the ``smart" learning algorithm will matter if the number of rounds is sufficiently high but for a low number of rounds, better initial information may be more important than a better learning algorithm.

\section*{Experiment 5 - Warm Start and HardMax}
What is the effect of a ``warm start" on the performance of HardMax? In this case we define a ``warm start" as giving the principal free observations (but do not change the information set of the agent). Our simulations show that with HardMax the initial rounds matter a lot in a particular simulation and whoever wins in the first few rounds takes the entire market. We explore if having a warm start makes it so that the market is more evenly split in a given simulation.\\
